Hydras \& Co.

### 2022-01-05 doc/part-hydras.tex
new title page
fix typos in chapter 2 and bibliography

\begin{itemize}
\item Semi automatic tactics for proving inequalities $\alpha < \beta$, even when $\alpha$ and $\beta$ are not closed terms.
\item Extension to $\Gamma_0$ (in Veblen normal form)
\item More lemmas about hierarchies of rapidly growing functioit ns, and their relationship 
    with primitive recursive functions and provability in Peano arithmetic 
(following~\cite{KS81, KP82}).
\item From \coq's point of view, this development could be used as an illustration of the evolution of the software, every time new libraries and sets of tactics could help to simplify the proofs.
\end{itemize}

@@

In order to describe trees where each node can have an arbitrary (but finite) number of sons, it is usual to define a type where each node carries a \emph{forest}, \emph{i.e} a list of trees
(see for instance Chapter 14, pages 400-406 of \cite{BC04}).

For this purpose, we define two mutual \emph{ad-hoc}  inductive types, where \texttt{Hydra} is the main type, and \texttt{Hydrae} is a helper for describing finite sequences of hydra.
\label{types:Hydra}
\label{types:Hydrae}

@@

Using this representation, re-define all the constructions of this chapter.
You will probably have to use patterns described for instance in~\cite{BC04} or the archives of the Coq-club~\cite{Coq}.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=11cm]{epsilon0.jpg}
  \caption{Veblen normal form}
  \label{fig:gamma0}
\end{figure}

>>>>

\begin{itemize}
\item Semiautomatic tactics for proving inequalities $\alpha < \beta$, even when $\alpha$ and $\beta$ are not closed terms.
\item Extension to $\Gamma_0$ (in Veblen normal form)
\item More lemmas about hierarchies of rapidly growing
  functions, and their relationship 
    with primitive recursive functions and provability in Peano arithmetic 
(following~\cite{KS81, KP82}).
\item From \coq's point of view, this development could be used as an illustration of the evolution of the software, every time new libraries and sets of tactics could help to simplify the proofs.
\end{itemize}

@@

In order to describe trees where each node can have an arbitrary (but finite) number of sons, it is usual to define a type where each node carries a \emph{forest}, \emph{i.e} a list of trees
(see for instance Chapter 14, pages 400-406 of \cite{BC04,BC04ch14}).

For this purpose, we define two mutual \emph{ad-hoc}  inductive types, where \texttt{Hydra} is the main type, and \texttt{Hydrae} is a helper for describing finite sequences of hydras.
\label{types:Hydra}
\label{types:Hydrae}

@@

Using this representation, re-define all the constructions of this chapter.
You will probably have to use patterns described for instance in~\cite{BC04} or the archives of the \coq communication channels (please consult~\url{https://coq.inria.fr/community.html}).

@@
